%!TEX root = planning.tex
\section{COCOMO: effort \& cost estimation}
\subsection{Overview} % (fold)
\label{sub:cocomo_overview}
The COCOMO II Cost Estimation Model is a complex estimation technique used 
by thousands of software engineers all over the world. \\
It's used to estimate the effort cost of a software engineering project.
The core of COCOMO II is the use of the Effort Equation to estimate the number
of Person/Month required to develop a complex project.

We have used this file as reference: \\ 
\url{http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII_modelman2000.0.pdf}

\subsection{Scale Drivers} % (fold)
\label{sub:scale_drivers}
% TODO tabella scale drivers

\paragraph{PREC} Precedentedness. \\ 
This driver reflects the previous experience that the developers have in this 
field. Actually, this is our first experience, so we think the best value for
our team is \emph{LOW}.

\paragraph{FLEX} Development flexibility. \\
This driver will change due to our flexibility degree in the development.
Our schedule is quite strict, so we choose \emph{LOW} for this project.

\paragraph{RESL} Risk resolution. \\
% TODO!!
It reflects the extension of the risk analysis. We choose 'generally'
because reasons. % <- TODO

\paragraph{TEAM} Team cohesion. \\
This value is correlated to how well the development team know each other. 
In this case we are a very cooperative team, so \emph{VERY HIGH} value is
our choice.

\paragraph{PMAT} Process maturity. \\
% TODO!!
Here there is the weighted average of ``Yes'' answers to CMM Maturity Questionnaire.
Let's Try with High, Level 3

Here is a sum of archieved results.

\begin{tabular}{ p{5cm} | c | c }
    Scale Driver            & Factor             &  Value   \\ \hline
    Precedentedness         & \texttt{LOW}       &  4.96    \\
    Development Flexibility & \texttt{LOW}       &  4.05    \\
    Risk Resolution         & \texttt{HIGH}      &  2.83    \\
    Team Cohesion           & \texttt{VERY HIGH} &  1.10    \\
    Proces Maturity         & \texttt{HIGH}      &  3.12    \\ \hline
    Total                   &                    & 16.06  
\end{tabular}

\subsection{Cost Drivers} % (fold)
\label{sub:cost_drivers}

\cost{RELY}{Required Software Reliability}
{Slight inconvenience}{Easily recoverable losses}{Easily recoverable losses}
{High financial loss}{Risk to human life}{}
{0.82}{0.92}{1.00}{1.10}{1.26}{n/a}
\paragraph{Database Size}
\paragraph{Product Complexity}
\paragraph{Required Reusability}
\paragraph{Documentation match to life-cycle needs}
\paragraph{Execution Time Constraint}
\paragraph{Main Storage Constraint}
\paragraph{Platform Volatility}
\paragraph{Analyst Capability}
\paragraph{Programmer Capability}
\paragraph{Application Experience}
\paragraph{Platform Experience}
\paragraph{Platform Experience}
\paragraph{Language and Tool Experience}
\paragraph{Personnell Continuity}
\paragraph{Usage of Software Tools}
\paragraph{Multisite Development}
\paragraph{Required development schedule}

% subsection cost_drivers (end)
% subsection scale_drivers (end)
\subsection{Effort Equation} % (fold)
\label{sub:effort_equation}
